---
title: "Long non coding RNAs are differentially expressed by age and exercise"
format: html
editor: visual
bibliography: references.bib
---

### Tentative Journals

https://www.sciencedirect.com/journal/mechanisms-of-ageing-and-development Level 1

https://rnajournal.cshlp.org/ Level 2

## Abstract

Only few long non-coding RNAs have been functionally annotated. We hope to determine age-associated patterns in lmcRNA from human skeletal muscle (*vastus lateralis*)

## Introduction

Genes can be broadly grouped into protein-coding and non-protein-coding genes. Among the non-protein-coding genes are are those described as "long non-coding RNA" genes typically made up of 200 nucleotides or more @ali2020 @marttila2020 and ere expressed at a much lower level lever compared to proteinc coding genes. They are tissue specific @ali2020 and show spatio temporal expression patterns @marttila2020. They are said to have an ability to intereact with DNA, RNA or protein . They regulate splicing, mRNA/protein stability and protein subcellular localization @he2019. Certain lncRNAs have been said to play roles in oncogenesis @he2019, in cardiovascular diseases @bink2019, type 2 diabetes @he2017

Previous studies have linked aging to expression patterns of certain lncRNAs @marttila2020 @bink2019

## 2. Materials and Methods

2.1 Data source

The data used in this study were obtained from the TrainOme group and consisted of RNA Sequence and metadata from three independent Resistance exercise studies all targetted at the *vastus lateralis* muscle

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
